---
title: "Ricardo"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#Install packages
install.packages('fpp2') #plot, timeseries
install.packages('xts') #convert timeseries data to dataframe
install.packages('knitr') #kable for table
install.packages('kableExtra') #kable extra for table
```

Stage 3 - Explore and Visualize Data

First we will load library and load the data.
```{r}
###Load Library
library(fpp2)
library(xts)
library(knitr)
library(kableExtra)

###Load Data
Tourist_Arrivals_Monthly_Malaysia_1_ <- read.csv("~/Algorithm/3121/Tourist Arrival.csv")

###Check Data
head(Tourist_Arrivals_Monthly_Malaysia_1_)
##Check Data Length
length(Tourist_Arrivals_Monthly_Malaysia_1_$Date)
##Check Data Maximum and Minimum Values
max(Tourist_Arrivals_Monthly_Malaysia_1_$Tourists.Arrival)
min(Tourist_Arrivals_Monthly_Malaysia_1_$Tourists.Arrival)
```


```{r}
#Detect Data Outliers
boxplot(Tourist_Arrivals_Monthly_Malaysia_1_$Tourists.Arrival,
        main = "Boxplot of Tourism Arrival",
        ylab = "Number of Tourism Arrival")
```
Overall, we can see that there is no outliers, indicated by no points that are above Q3 + 1.5 * IQR or below the Q1 - 1.5 * IQR of the data distribution

```{r}
#Check Missing Values
Tourist_Arrivals_Monthly_Malaysia_1_ %>% is.na() %>% sum()
```
So, there is also no missing value indicated in the Tourism Data.

WE will continue to plot the data to better see trends in the data.
```{r}
#Convert to time-series data
tourist <- ts(Tourist_Arrivals_Monthly_Malaysia_1_$Tourists.Arrival, frequency =12, start= c(1989,1))

#Then we visualize our data to chart
autoplot(tourist) + 
  ylab("Number of Tourist Arrival") + 
  ggtitle('Time Series Plot of Monthly Tourist Arrival In Malaysia')

#Plot with geom smooth to see average trend
autoplot(tourist) +geom_smooth() +
  ylab("Number of Tourist Arrival") + 
  ggtitle('Time Series Plot of Monthly Tourist Arrival In Malaysia with Smoothed Graph')
```

```{r}
ggsubseriesplot(tourist)+
  ylab("Number of Tourist Arrival") + 
  ggtitle('Subseriesplot of Monthly Tourist Arrival In Malaysia')
```

```{r}
ggseasonplot(tourist)+
  ylab("Number of Tourist Arrival") + 
  ggtitle('Seasonality plot of Monthly Tourist Arrival In Malaysia')
```


```{r}
#Plot ggAcf
ggAcf(tourist) + 
  ggtitle('ACF plot of Monthly Tourist Arrival In Malaysia')
```


```{r}
#Determine full dataset
full_dataset <- window(tourist, start= c(2005,01), end=c(2021,03))

#Plot our final full_dataset
autoplot(full_dataset) + 
  ylab("Number of Tourist Arrival") + 
  ggtitle('Full Data Set')
```


Stage 5 
Split our data to precovid data and postcovid data
Pre-covid - Jan 2005 - Jan 2020
Covid - Feb 2020 - march 2021

```{r}
#Data split for precovid and postcovid
precovid <- window(tourist, start= c(2005,01), end=c(2020,01))
covid <- window(tourist, start=c(2020,02), end=c(2021,03))
```

```{r}
#Plot precovid data to better understand the trend of Malaysia tourism before COVID
autoplot(precovid) + 
  ylab("Number of Tourist Arrival") + 
  ggtitle('Time Series Plot of Monthly Tourist Arrival In Malaysia before COVID-19')
```


Divide precovid dataset into training and test set (80/20)- state the length 
```{r}
# Dividing precovid data to train set and test set
precovid.train <- window(precovid, end = c(2017,1)) # 80
precovid.test <- window(precovid, start= c(2017,2)) # 20 

#Check Train set and Test set
precovid.train
precovid.test

#Check number of observation for each set
length(precovid.train)
length(precovid.test)
```

```{r}
#Then we plot precovid.train to better understand the trend to select the method/models
autoplot(precovid.train) + 
  ylab("Number of Tourist Arrival") + 
  ggtitle('Time Series Plot of Monthly Tourist Arrival In Malaysia for Training Data')
```


```{r}
#Decomposition to see better components of our training data.
precovid.train %>% decompose() %>% plot()
```


Stage 6 

The models that we are using are Drive method, ETS MAdM model, and ETS MAdN model.
```{r}
#Simple Forecasting Method

### We choose to do Random Walk Drift, as the training set of data clearly indicates that there is overall linear upward trend, despite the variance changes overtime.
### Fit Drift Method in Training Set
RWD <- rwf(precovid.train, drift = TRUE) 
summary (RWD)

#Fitted RWD
RWD.fit <- fitted(RWD)
```


```{r}
# ETS 1 model (MAdM)
ETS.1<- ets(precovid.train, model = "MAM", damped= TRUE)
summary (ETS.1)

#Fitted ETS 1
ETS.1.fit <- fitted(ETS.1)
```


```{r}
# ETS 2 model (M Ad N)
ETS.2<- ets(precovid.train, model = "MAN", damped= TRUE)
summary (ETS.2)

#Fitted ETS 2
ETS.2.fit <- fitted(ETS.2)
```

Use the ETS function in R to automatically set an ETS model 
```{r}
# ETS default
ETS.3 <- ets(precovid.train)
summary(ETS.3)

#We do not fit this ETS model as it correlates with the previously mentioned M Ad M model.
```

Table for summary measures (parametres estimates, initial values, summary measures)
```{r}
###Create dataframe
Variables <- c("alpha","beta","gamma","phi","l","b","s","sigma","AIC", "AICc", "BIC", "RMSE")
M_Ad_M <- c(0.5332, 0.0016, 1e-04, 0.98, 1348745.2912, 18260.3124, "1.1057, 0.9963, 1.0058, 0.9625, 1.0064, 1.0353,
           1.0045, 0.973, 0.9565, 1.0328, 0.9151, 1.0059", 0.0614, 4126.835, 4132.264, 4180.416, 115552.2)
M_Ad_N <- c(0.2665, 0.0027, "-", 0.98, 1373446.5121, 2728.4409, "-", 0.0805, 4192.281, 4192.890, 4210.142, 159485.2)
Table_summary <- data.frame(Variables, M_Ad_M, M_Ad_N)
Table_summary
```

```{r}
###Create Table
Table_summary %>%
  kbl(caption = "Estimated Smoothing Parameters Summary") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```


Produce separate plots of the training set data with the fitted values from each models
```{r}
#Random Walk Drift Plot
autoplot(precovid.train, series = "Training Data") + 
  xlab("Year") +
  ylab("Number of Tourist Arrival in Malaysia") +
  ggtitle("Within Sample Forecast against Training Data") +
  autolayer(RWD.fit, series = "Random Walk Drift Method")  

#ETS (M Ad M) Plot
autoplot(precovid.train, series = "Training Data") + 
  xlab("Year") +
  ylab("Number of Tourist Arrival in Malaysia") +
  ggtitle("Within Sample Forecast against Training Data") +
  autolayer(ETS.1.fit, series = "ETS(M Ad M)")

#ETS (M Ad N) Plot
autoplot(precovid.train, series = "Training Data") + 
  xlab("Year") +
  ylab("Number of Tourist Arrival in Malaysia") +
  ggtitle("Within Sample Forecast against Training Data") +
  autolayer(ETS.2.fit, series = "ETS(M Ad N)")
```

Residual Diagnostic Checks

```{r}
checkresiduals(RWD) # Random Walk Drift
checkresiduals(ETS.1) #Multiplicative Holt-Winters' Method Damped with Multiplicative Errors
checkresiduals(ETS.2) #Holt Method with Multiplicative Errors
```
Best Goodness of Fit : ETS.1

Based on the three models/methods that have been used in doing the within sample forecast, we will apply the same models to the test set, generating Out-of-Sample Forecast.

Forecast is produced using test set
```{r}
# Drift Method 
RWD.fc <- rwf(precovid.train, drift = TRUE, h = length(precovid.test))

## ETS(M Ad M) Model

ETS.1.fc <-forecast(ETS.1, h=length(precovid.test))

## ETS(M Ad N) Model
ETS.2.fc <- forecast(ETS.2, h=length(precovid.test))
```

Plot our forecast for the test set
```{r}
# Forecast Random Walk Drift Plot
autoplot(precovid, series= "Full dataset") +
  xlab("Years") +
  ylab("Number of Tourist Arrivals in Malaysia") +
  ggtitle("Forecast of Test Set with Random Walk Drift") +
  autolayer(RWD.fc, series = "Random Walk Drift Method", PI = FALSE) 
 
# Forecast ETS (M A M) Plot
autoplot(precovid, series= "Full dataset") +
  xlab("Years") +
  ylab("Number of Tourist Arrivals in Malaysia") +
  ggtitle("Forecast of Test Set with ETS(M Ad M) Model") +
  autolayer(ETS.1.fc, series ="M Ad M", PI = FALSE) 

# Forecast ETS (M Ad N) Plot
autoplot(precovid, series= "Full dataset") +
  xlab("Years") +
  ylab("Number of Tourist Arrivals in Malaysia") +
  ggtitle("Forecast of Test Set with ETS(M Ad N) Model") +
  autolayer(ETS.2.fc, series = "M Ad N", PI = FALSE)
```

Stage 7 : Evaluate and Compare Forecasting Performance 

Traditional Approach using the out-of-sample forecast accuracy
```{r}
#Out of sample forecast accuracy for Random Walk Drift 
accuracy(RWD.fc, precovid.test)

#Out of sample forecast accuracy for ETS (M Ad M)
accuracy(ETS.1.fc, precovid.test)

#Out of sample forecast accuracy for ETS (M Ad N)
accuracy(ETS.2.fc, precovid.test)
```


Modern Approach 
```{r}
#### For h = 1
# Error in Cross-Val method for Random Walk Drift
e.rwf <- tsCV(precovid.train, rwf, h=1)

# Error in Cross-Val method for ETS (M Ad M)
f.1 <- function(y,h)   {forecast(ets(y,model = "MAM", damped = TRUE),h= h)} # ETS.1
e.ETS.1 <- tsCV(precovid.train, f.1, h=1)

# Error in Cross-Val method for ETS (M Ad N)
f.2 <- function(y,h)   {forecast(ets(y,model = "MAN", damped = TRUE),h= h)} # ETS.2
e.ETS.2 <- tsCV(precovid.train, f.2, h=1)
```

```{r}
#### For h = 12
# Error in Cross-Val method for Random Walk Drift
e.rwf_ <- tsCV(precovid.train, rwf, h=12)

# Error in Cross-Val method for ETS (M Ad M)
f.1_ <- function(y,h)   {forecast(ets(y,model = "MAM", damped = TRUE),h= h)} # ETS.1
e.ETS.1_ <- tsCV(precovid.train, f.1_, h=12)

# Error in Cross-Val method for ETS (M Ad N)
f.2_ <- function(y,h)   {forecast(ets(y,model = "MAN", damped = TRUE),h= h)} # ETS.2
e.ETS.2_ <- tsCV(precovid.train, f.2_, h=12)
```

To compute MSE from h=1 to h=12
```{r}
# Modern Approach MSE for Random Walk Drift
colMeans(e.rwf_^2, na.rm = TRUE)

# Modern Approach MSE for ETS (M Ad M)
colMeans(e.ETS.1_^2, na.rm = TRUE)

# Modern Approach MSE for ETS (M Ad N)
colMeans(e.ETS.2_^2, na.rm = TRUE)
```


Compute RMSE 
```{r}
###For h = 1
# Modern Approach RMSE for Random Walk Drift
mean(e.rwf^2, na.rm = TRUE) %>% 
  sqrt()

# Modern Approach RMSE for ETS (M Ad M)
mean(e.ETS.1^2, na.rm = TRUE) %>% 
  sqrt()

# Modern Approach RMSE for ETS (M Ad N)
mean(e.ETS.2^2, na.rm = TRUE) %>%
  sqrt()

```

```{r}
###For h = 12
# Modern Approach RMSE for Random Walk Drift
mean(e.rwf^2, na.rm = TRUE) %>% 
  sqrt()

# Modern Approach RMSE for ETS (M Ad M)
sqrt(mean(e.ETS.1_^2, na.rm = TRUE))
 

# Modern Approach RMSE for ETS (M Ad N)
mean(e.ETS.2_^2, na.rm = TRUE) %>%
  sqrt()
```


Stage 8 : Implement Forecast

```{r}
# Apply to the full pre-covid dataset
#Re-estimate our parameter using precovid data set.
ETS.1.fulldata <- ets(precovid, model = "MAM", damped= TRUE)
summary (ETS.1.fulldata)
```

```{r}
###Create dataframe
Variables <- c("alpha","beta","gamma","phi","l","b","s","sigma","AIC", "AICc", "BIC", "RMSE")
Final_Model <- c(0.5347, 1e-04, 1e-04, 0.9796, 1346393.6713, 18344.8017, "1.0939, 0.9744, 0.9985, 0.9599, 1.0112, 1.0473
           1.0151, 0.9679, 0.9568, 1.0334, 0.9299, 1.0117", 0.0595, 5184.288, 5188.510, 5241.861, 115372.1)
Table_summary.fm <- data.frame(Variables, Final_Model)
Table_summary.fm
```

```{r}
###Create Table
Table_summary.fm %>%
  kbl(caption = "Estimated Smoothing Parameters Summary for Final Model") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```

```{r}
#Plot of Final Model Forecast
ETS.1.fulldata.fc <-forecast(ETS.1.fulldata, h=length(covid), c(68, 95)) ## use rule of thumb to get the prediction interval
autoplot(ETS.1.fulldata.fc) +
  xlab("Year") +
  ylab("Number of Tourist Arrival in Malaysia") +
  ggtitle("Forecast During COVID-19 Period")
```
```{r}
#Summary of the model
summary(ETS.1.fulldata.fc)
```

```{r}
#Plot of Final Model Forecast Compared to Actual Data During COVID-19
autoplot(full_dataset)+
  autolayer(ETS.1.fulldata.fc) +
  xlab("Year") +
  ylab("Number of Tourist Arrival in Malaysia") +
  ggtitle("Forecast During COVID-19 Period")
```

Stage 9: Quantifying Forecasted Loss in tourism Revenue 

To calculate the forecasted loss, we have to calculate the difference in the forecasted tourist number compared to the acutal number after Covid pandemic.

```{r}
#To obtain forecasted number
FC <- summary(ETS.1.fulldata.fc)
#Turn the data to data frame
FC.df <- data.frame(FC)
FC.df
```

```{r}
#To obtain the actual tourism number
dataset_covid <- as.xts(covid)
dataset_covid <- data.frame(dataset_covid)
dataset_covid
```

First, we calculate average forecasted loss in RM 
```{r}
#Then, we calculate the difference in the forecasted and the actual tourism number for each month 
difference <- FC.df$Point.Forecast - dataset_covid$dataset_covid
difference
```

```{r}
#Finally, we calculate the total number of tourism loss due to COVID
sum(difference)
```

```{r}
#We then calculate the forecasted tourism revenue loss in dollar
((851+843+783+736+746)/5) * sum(difference)
#Assuming exchange rate of 4.15RM/$ (per September 13th)
((851+843+783+736+746)/5) * sum(difference) * 4.15
```

Then, we calculate range of forecasted loss in RM, with 95% confidence level

```{r}
#For upper limit
differenceup <- FC.df$Hi.95 - dataset_covid$dataset_covid
differenceup
```

```{r}
#For lower limit
differencebelow <- FC.df$Lo.95 - dataset_covid$dataset_covid
differencebelow
```

```{r}
#Calculate the total number of tourism loss for both upper and lower limit
sum(differenceup)
sum(differencebelow)
```

```{r}
#We then calculate the forecasted tourism revenue loss in dollar for both upper and lower limit
((851+843+783+736+746)/5) * sum(differenceup)
((851+843+783+736+746)/5) * sum(differencebelow)
#Assuming exchange rate of 4.15RM/$ (per September 13th)
((851+843+783+736+746)/5) * sum(differenceup) * 4.15
((851+843+783+736+746)/5) * sum(differencebelow) * 4.15
```
